A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-24 paper/paper.tex
referring to fig 3 for examples

As a side remark, note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.

>>>>

Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore. For instance, it produces figure \ref{fig:intuition} for $n=2$ and $\nu=2$.
